---
title: "Model 2 analysis"
author: "Benjamin Mercier"
date: "`r paste('Last updated on', format(Sys.time(), '%d %B, %Y'))`"
---

<!-- Load nedeed libraries -->
```{r, echo = FALSE, message=FALSE, warning=FALSE}
suppressPackageStartupMessages(library(rstan))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(tidybayes))
suppressPackageStartupMessages(library(bayesplot))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(ggdist))
suppressPackageStartupMessages(library(ggridges))
suppressPackageStartupMessages(library(hrbrthemes))
suppressPackageStartupMessages(library(viridis))
```
<!-- Load the data --> 
```{r load_model1, echo = FALSE, fig.height=15, fig.width=10}
dataset <- readRDS("../data/clean/new_dataset.RDS")
output_stan_model2 <- readRDS("../results/model_outputs/output_stan_model2.RDS")
```

# Model 2
## Description of the model
<br>
This second model is a slight variant of the first, in which we assign a specific $\alpha$ to each predator. In doing so, we can isolate difference between predator, to check if some predator seems to be different from the whole.
<!-- Model equation -->
\begin{align}
F_{ij}^{real} &= \alpha_{j} * B_i * \frac{B_j}{M_j}
\end{align}

This model was fit with a hierarchy implemented on the alpha parameter. A global alpha was estimated, with 118 respective unique alphas for each predators.

```{r structure_data, echo = FALSE}
# Recover types
output_stan_model2 <- recover_types(output_stan_model2)
# Draw the posterior for all parameters
general_params <- output_stan_model2 |>
                   tidybayes::gather_draws(a_pop, a_sd, sigma)

a_grp <- output_stan_model2 |> tidybayes::gather_draws(a_grp[pred_id])
         # dplyr::arrange(pred_id)
          #dplyr::mutate(pred_id = as.factor(pred_id))

# Get pred_id & habitat_type to join with the stan output
pred_ids <- unique(dataset[, c("pred_id", "habitat_type")])
a_grp <- dplyr::left_join(a_grp, pred_ids, by = "pred_id") |>
          dplyr::arrange(pred_id) |>
          dplyr::mutate(pred_id = as.factor(pred_id))
#alphas2_mean <- plyr::ddply(alphas2, "parameters", dplyr::summarise, grp.mean = mean(value))
#other_params2_mean <- plyr::ddply(other_params2, "parameters", dplyr::summarise, grp.mean = mean(value)) |> dplyr::filter(!parameters %in% c("lp__"))
```

## Exploring parameters posterior distribution
### General parameters
```{r general-ridgeplots, echo=FALSE, message=FALSE, fig.height=12, fig.width=10}
# Plot the global parameters
general_params |>
  ggplot(aes(x = `.value`, y = `.variable`)) +
  geom_density_ridges_gradient(scale = 1, rel_min_height = 0.0001, fill = "lightskyblue3") +
  labs(title = "Posterior distribution of global parameters") +
  theme_ipsum() +
  theme(
    legend.position = "none",
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    plot.title = element_text(size = 30),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15)
  ) +
   xlab("log-values") +
   ylab("Parameter ID")
```

### Respective predator alphas
```{r alphas-ridgeplots, echo=FALSE, message=FALSE, fig.height=18, fig.width=15}
# Plot the unique alphas by predator
ggplot(a_grp, aes(x = `.value`, y = pred_id, fill = habitat_type)) +
  geom_density_ridges_gradient(scale = 5, rel_min_height = 0.01) +
   #scale_fill_viridis(option = "C") +
    labs(title = "Posterior distribution of predators alpha") +
     theme_ipsum() +
      theme(
       legend.title = element_text(size = 15),
       legend.text = element_text(size = 13),
       axis.title.y = element_text(size = 20),
       axis.title.x = element_text(size = 20),
       plot.title = element_text(size = 30),
       axis.text.x = element_text(size = 15),
       axis.text.y = element_text(size = 15)
      ) +
       ylab("Parameters ID") +
       xlab("log-values") +
        scale_y_discrete(guide = guide_axis(n.dodge = 2)) +
         scale_fill_manual("Ecosystem type",values = c("terrestrial" = "olivedrab",
          "freshwater" = "sandybrown", "marine" = "deepskyblue3","marine_freshwater" = "slateblue4")) 

```

## Rhats
### Examining Rhats to see if all parameters have converge
```{r rhats, echo=FALSE, message=FALSE}
rhat(output_stan_model2) |>
mcmc_rhat_hist()
```

```{r traceplots, echo=FALSE, eval = FALSE}
#color_scheme_set("mix-brightblue-gray")
#np_cp <- nuts_params(output_stan_model2)
#mcmc_trace(output_stan_model2, pars = c("a_pop","a_sd","sigma"), np = np_cp) + xlab("Post-warmup iteration")
#mcmc_trace(output_stan_model2, pars = vars(param_range("a_grp", range = c(1:20))), np = np_cp) + xlab("Post-warmup iteration")
#mcmc_trace(output_stan_model2, pars = vars(param_range("a_grp", range = c(21:40))), np = np_cp) + xlab("Post-warmup iteration")
#mcmc_trace(output_stan_model2, pars = vars(param_range("a_grp", range = c(41:60))), np = np_cp) + xlab("Post-warmup iteration")
#mcmc_trace(output_stan_model2, pars = vars(param_range("a_grp", range = c(61:80))), np = np_cp) + xlab("Post-warmup iteration")
#mcmc_trace(output_stan_model2, pars = vars(param_range("a_grp", range = c(81:100))), np = np_cp) + xlab("Post-warmup iteration")
#mcmc_trace(output_stan_model2, pars = vars(param_range("a_grp", range = c(101:118))), np = np_cp) + xlab("Post-warmup iteration")
```
